---
title: "Experiment Report"
author: "Kadir Korkmaz"
date: "`r commandArgs(trailingOnly=T)[3]`"
output:
  pdf_document: default
  fig_width: 6 
  fig_height: 2 
---


```{r setup, include=FALSE}

# How to run r file from commandline by providing arguments
# R -e "rmarkdown::render('experiment-report-1.rmd', output_file='hello.pdf')" --args /Users/kadir/Git/experiment-automation/output/stats/2021-03-08_07:00:00 /Users/kadir/Git/experiment-automation/config.json 15.04.1989

# source: https://stackoverflow.com/questions/31463143/pass-parameters-from-command-line-into-r-markdown-document

# First argument the path of the folder which contains the stat files
# Second argument is the path of config file
# Third argument a timestamp to show in the cover of the report

# The report will renamed according to Macroblock size and concurrency constant comming from config file
cmd_args <- commandArgs(trailingOnly=T)

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)

#install.packages("data.table", repos = "https://cran.rstudio.com")
library(data.table)

# Folder which contains *.stat files
dataFolderPath <- cmd_args[1]
# The path of config file
path_of_config <- cmd_args[2]

# Lists all stat files
list_of_files <- list.files(path = dataFolderPath, recursive = TRUE, pattern = "\\.stat$",  full.names = TRUE)


# Read all the files and create a FileName column to store filenames
DT <- rbindlist(sapply(list_of_files, fread, simplify = FALSE),
                use.names = FALSE, idcol = "FileName")


#Data set contains to kinds of data, we are organizing data

experiment_df <- as.data.frame(DT)

colnames(experiment_df)[1] = "FileName"
colnames(experiment_df)[2] = "Date"
colnames(experiment_df)[3] = "Time"
colnames(experiment_df)[4] = "Data"

experiment_df$FileName <- basename(experiment_df$FileName)

stats_df <- experiment_df %>% filter(str_detect(Data, 'stats'))
stats_sp <- separate(data = stats_df, col = Data, into = c(
              "Type",
              "NodeID",
              "MacroBlockSize",
              "CC",
              "Round",
              "BlockPropagation", 
              "BAWithOutFinalStep",
              "BAWithFinalStep",
              "ConsensusType",
              "BlockType",
              "BlockHash",
              "PayloadSize",
              "ElectedAsLeader"
              ), convert = TRUE, sep = "\\\t")

stats_sp$FileName <- stats_df$FileName

message_df <- experiment_df %>% filter(str_detect(Data, 'messages'))
message_df <- separate(data = message_df, col = Data, into = c("Type","Round","BlockCount", "ProposalCount","VoteCount"), convert = TRUE, sep = "\\\t")


upload_df <- experiment_df %>% filter(str_detect(Data, 'upload-stat'))
upload_df <- separate(data = upload_df, col = Data, into = c("Type","Receiver","MessageLength", "ElapsedTime"), convert = TRUE, sep = "\\\t")

experiment_df <- stats_sp[, c("FileName", "Type", "NodeID", "MacroBlockSize",  "CC",  "Round", "BlockPropagation", "BAWithOutFinalStep", "BAWithFinalStep","ConsensusType", "BlockType","BlockHash", "PayloadSize", "ElectedAsLeader")]

number_of_machines <- nrow( experiment_df %>% group_by(FileName) %>% summarise(count = n()) )


#install.packages("readr")
library(readr)
#install.packages("jsonlite")
library(jsonlite)


path_of_config_file=

node_condiguration <- read_file(path_of_config)
nodeo_config_df <- fromJSON(node_condiguration)


```


# Experiment Configuration



Advanced algorand with concurrency constant **`r nodeo_config_df$BAStar$ConcurrencyConstant` **

Number of nodes is **`r nodeo_config_df$NodeCount` **

Bandwidth limit per process using Trickle: **20 Mbps using tc and cgroups**

tc Delay on outgoing channel: **50 ms delay (RTT 100ms)**

\newpage
## Node Configuration

```{r, echo=FALSE}

prettify(node_condiguration, indent = 4)


```


\newpage
# Sanity Check

```{r, echo=FALSE, fig.width=8}

library(knitr)

sanity_df <- experiment_df %>% 
              group_by(FileName) %>%
              summarise(
                count = n(),
                mean_bp = mean(BlockPropagation, na.rm=TRUE),
                mean_ba_wo_final = mean(BAWithOutFinalStep, na.rm=TRUE),
                mean_ba_w_final = mean(BAWithFinalStep, na.rm=TRUE),
                distinct_hash=n_distinct(BlockHash),
                max_round = max(Round)
              )

kable(sanity_df)

block_stats_df <- experiment_df %>% 
                  group_by(Round) %>%
                    summarise(
                      payload_size = mean(PayloadSize, na.rm=TRUE),
                      payload_size_mb = mean(PayloadSize, na.rm=TRUE) / 1000000
                    )


library(ggplot2)

ggplot(block_stats_df, aes(x=Round, y=payload_size)) + geom_point(stat = "identity")


```

The number of rows in data set is **`r nrow(experiment_df)`**

Maximum round number is **`r max(experiment_df$Round)`**

Appended payload size is is **`r sum(block_stats_df$payload_size_mb)`** MB

\newpage
# Overal Results

```{r, echo=FALSE}

boxplot(experiment_df[7:9],
  main = "",
  xlab = "Step",
  ylab = "Seconds",
  col = "orange",
  border = "brown",
  horizontal = FALSE,
  notch = FALSE
)



kable(caption="Summaries", summary( experiment_df[7:9]))


```




\newpage
# Block Propagation Statistics

```{r, echo=FALSE}

hist(experiment_df$BlockPropagation, main="", xlab = "")

```

```{r, echo=FALSE}

boxplot(experiment_df$BlockPropagation,
  main = "",
  xlab = "Seconds",
  ylab = "Block Propagation",
  col = "orange",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

```

\newpage
# BA Elapsed Time Without Final Step Statistics


```{r, echo=FALSE}

hist(experiment_df$BAWithOutFinalStep, main="", xlab = "")

```

```{r, echo=FALSE}

boxplot(experiment_df$BAWithOutFinalStep,
  main = "",
  xlab = "Seconds",
  ylab = "BA Without Final Step",
  col = "orange",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

```



\newpage
# BA Elapsed Time With Final Step Statistics

```{r, echo=FALSE}

hist(experiment_df$BAWithFinalStep, main="", xlab = "")

```

```{r, echo=FALSE}

boxplot(experiment_df$BAWithFinalStep,
  main = "",
  xlab = "Seconds",
  ylab = "BA With Final Step",
  col = "orange",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

```


\newpage
# Forwarded Message Counts Per Round

```{r, echo=FALSE, fig.height=3}

boxplot(message_df$BlockCount,
  main = " ",
  xlab = "",
  ylab = "Block Count",
  col = "orange",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

boxplot(message_df$ProposalCount,
  main = " ",
  xlab = "",
  ylab = "Proposal Count",
  col = "orange",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)


boxplot(message_df$VoteCount,
  main = " ",
  xlab = "",
  ylab = "Vote Count",
  col = "orange",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)


```



\newpage
# Block Upload Stats
```{r, echo=FALSE, fig.height=3}

hist(upload_df$ElapsedTime, main="", xlab = "", breaks = 20 )


summary( upload_df$ElapsedTime)

boxplot(upload_df$ElapsedTime,
  main = " ",
  xlab = "",
  ylab = "",
  col = "orange",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

summary( upload_df$MessageLength)


grouped <- upload_df %>% group_by(FileName) %>% summarise(Count = n(), Min = min(ElapsedTime), Mean=mean(ElapsedTime), Max=max(ElapsedTime))

kable(grouped)

sum(grouped$Count)


```

# Leader count per round
```{r, echo=FALSE}

leaderCountsPerRound <- experiment_df %>% 
                        group_by(Round) %>%
                        summarise( LeaderCount = sum(ElectedAsLeader == "true"))

hist(leaderCountsPerRound$LeaderCount, labels = TRUE, breaks = 10)

summary(leaderCountsPerRound$LeaderCount)


macroBlockSizePerRound<- experiment_df %>% distinct(Round, .keep_all= TRUE) %>% 
                        group_by(PayloadSize) %>%
                        summarise( Count = n())

head(macroBlockSizePerRound)



```




